---
title: "Salt_ProjectAkhir"
author: "Deswina"
date: '2022-07-25'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(readxl)
library(lubridate)
library(dplyr)
library(googlesheets4)
library(tidyverse)
library(naniar)
```

    ### Extract

#Read file
```{r}
post <- read_xlsx("Data/ProjectAkhir/Post.xlsx")
follower_2021 <- read_excel("Data/ProjectAkhir/Follower Brand Data.xlsx", sheet = "Follower Brand Data (2021)")
follower_2022 <- read_excel("Data/ProjectAkhir/Follower Brand Data.xlsx", sheet = "Follower Brand Data")
```


    
    ### Transform



## POST DATA


#Try to count the total post of every brands and grouping by Page
```{r}
post %>% 
  group_by(Page) %>% 
  count()
```
#Filter the data based on Page 
```{r}
df_post <- post %>% 
  filter(Page == "Avoskin's Official Instagram" | Page == "avoskinbeauty" | Page == "elsheskin" | Page == "ELSHESKIN" | Page == "Healthy Skin Beautiful Skin" |
           Page == "SOMETHINC" |  Page == "somethincofficial" |  Page == "ElshéSkin" )
```

#Change Variable Name
```{r}
df_post <- df_post %>% 
  mutate(Name = ifelse(Page == "Avoskin's Official Instagram", "Avoskin_Instagram",
                                ifelse(Page == "avoskinbeauty", "Avoskin_Tiktok",
                                       ifelse(Page == "elsheskin", "Elsheskin_Tiktok",
                                              ifelse(Page == "Healthy Skin Beautiful Skin" |Page == "ELSHESKIN" | Page ==  "ElshéSkin", "Elsheskin_Instagram",
                                                     ifelse(Page == "SOMETHINC", "Somethinc_Instagram",
                                                             "Somethinc_Tiktok"
                                                     )))))) %>% 
  select(-Page)
```

#Check Missing Value in df_post
```{r}
miss_var_summary(df_post)
```

#Check Duplicated in df_post
```{r}
sum(duplicated(df_post))
```
Drop Duplicated Data
```{r}
df_post <- df_post %>% 
  unique()
```

#Check NA in Messgae Variable
```{r}
df_post %>% 
  filter(is.na(Message))
```

#Fill NA in Messages Variable with "NO CAPTION"
```{r}
df_post$Message[is.na(df_post$Message)] <- "NO CAPTION"
```

#Make New Variables to store the new data and change the `Comments and Likes (organic)` into Engagement.
#Drop `Comments (organic)`, `Likes (organic)`
```{r}
df_post <- df_post %>% 
  mutate(Engagement = `Comments and Likes (organic)`) %>% 
  select(-`Comments (organic)`, -`Likes (organic)`, -`Comments and Likes (organic)`)  %>% 
  relocate(Engagement, .after = `Number of Comments (total)`)
```

#Fill NA in Engagement Variable with the value of the sum of the variables `Number of Likes` and `Number of Comments (total)`
```{r}
i1 <- is.na(df_post$Engagement)

df_post$Engagement[i1] <- with(df_post, `Number of Likes`[i1] + `Number of Comments (total)`[i1])
```

#Check Missing Value in df_post
```{r}
miss_var_summary(df_post)
```

#Convert Date into GMT +7
```{r}
df_post <- df_post %>% 
  mutate(Date = Date + hours(7))
```
 
  ## Feature Engineering
  

#add Time Background variable
```{r}
df_post <- df_post %>% 
  mutate(Hour = hour(Date)) %>% 
  
  mutate('Time Background' = ifelse(Hour == 6 | Hour == 7 | Hour == 8 | Hour == 9 | Hour == 10 | Hour == 11,
                                "Morning",
                                ifelse(Hour == 12 | Hour == 13 | Hour == 14 | Hour == 15 | Hour == 16 | Hour == 17, "Afternoon",
                                       ifelse(Hour == 18 | Hour == 19 | Hour == 20 | Hour == 21, "Evening" , 
                                              "Night")))) %>% 
   relocate(Hour, .after = Date) %>% 
   relocate(`Time Background`, .after = Hour)
```

#add Hours Variable
```{r}
df_post <- df_post %>% 
  mutate(Hour = hour(Date)) %>% 
  relocate(Hour, .after = Date)
```


## DF FOLLOWER



#Merge follower_2021 and follower_2022 into one variable (Follower)
```{r}
follower <- rbind(follower_2021,follower_2022)
```

#Summary Follower
```{r}
summary(follower)
```
#Filter the data base on variable
```{r}
df_follower <- follower %>% 
  select(Date, `Avoskin Beauty`, `Avoskin's Official Instagram`, SOMETHINC, `Somethinc Official`, ELSHESKIN, ElsheSkin) %>% 
  mutate(Avoskin_Tiktok = `Avoskin Beauty`, Avoskin_Instagram = `Avoskin's Official Instagram`, Somethinc_Tiktok = `Somethinc Official`, Somethinc_Instagram = SOMETHINC,
         Elsheskin_Instagram = ELSHESKIN, ELsheskin_TIktok = ElsheSkin) %>% 
  select(-`Avoskin Beauty`, -`Avoskin's Official Instagram`, -SOMETHINC, -`Somethinc Official`, -ELSHESKIN, -ElsheSkin)
```

#Check Duplicated in df_follower
```{r}
sum(duplicated(df_follower))
```
#Drop DUplicated Data in df_follower
```{r}
df_follower <- df_follower %>% 
  unique()
```


#Check Missing Value in df_follower
```{r}
miss_var_summary(df_follower)

df_follower
```

#Check Missing Value in Somethinc_Tiktok
```{r}
df_follower %>% 
  select(Date, Somethinc_Tiktok)
```

#Fill Na in df_follower
```{r}
df_follower <- df_follower %>% 
  fill(Somethinc_Tiktok, .direction = "down") %>% 
  fill(Avoskin_Tiktok, .direction = "down") %>% 
  fill(ELsheskin_TIktok, .direction = "down")
  
```
#Check Value 0 in df_follower
```{r}
df_follower %>% 
  filter(Avoskin_Tiktok == 0 | Avoskin_Instagram == 0 |  Somethinc_Tiktok == 0 | Somethinc_Instagram == 0 | Elsheskin_Instagram == 0 | ELsheskin_TIktok == 0)

```
#Change value 0 into nilai dari baris diatasnya
```{r}
df_follower <- df_follower %>% 
  mutate(Somethinc_Tiktok = ifelse(Somethinc_Tiktok == 0, NA,
                                   Somethinc_Tiktok)) %>% 
   fill(Somethinc_Tiktok, .direction = "down")
  
```

#Check Missing Value in df_follower
```{r}
miss_var_summary(df_follower)
```

#Make new variable named Different that comes from the difference of followers per day
```{r}
##Avoskin
df_follower <- df_follower %>% 
  mutate(`Growth_av_tt` = `Avoskin_Tiktok`-lag(`Avoskin_Tiktok`)) %>% 
  relocate(Growth_av_tt, .after = Avoskin_Tiktok)

df_follower <- df_follower %>% 
  mutate(`Growth_av_ig` = `Avoskin_Instagram`-lag(`Avoskin_Instagram`)) %>% 
  relocate(Growth_av_ig, .after = Avoskin_Instagram)


##Somethinc
df_follower <- df_follower %>% 
  mutate(`Growth_so_tt` = `Somethinc_Tiktok`-lag(`Somethinc_Tiktok`)) %>% 
  relocate(Growth_so_tt, .after = Somethinc_Tiktok)

df_follower <- df_follower %>% 
  mutate(`Growth_so_ig` = `Somethinc_Instagram`-lag(`Somethinc_Instagram`)) %>% 
  relocate(Growth_so_ig, .after = Somethinc_Instagram)


##Elsheskin
df_follower <- df_follower %>% 
  mutate(`Growth_el_tt` = `ELsheskin_TIktok`-lag(`ELsheskin_TIktok`)) %>% 
  relocate(Growth_el_tt, .after = ELsheskin_TIktok)

df_follower <- df_follower %>% 
  mutate(`Growth_el_ig` = `Elsheskin_Instagram`-lag(`Elsheskin_Instagram`)) %>% 
  relocate(Growth_el_ig, .after = Elsheskin_Instagram)

```





    ### Load Data





#Input JSON from API Key.
```{r}
gs4_auth(path = "my_api_key.json")
```

#Assign the Docs into Variable gsheets.
```{r}
gsheet <- gs4_get("https://docs.google.com/spreadsheets/d/1S76OPrihc4NB52MzR7jsLZNGIrrak8HeIOnmMwucYhs/edit#gid=1383616703")
```

#Put the Data to the Sheets in the test Google Sheets we have.
```{r}
range_write(gsheet,
            df_post,
            sheet = "DF_Post")
range_write(gsheet,
           df_follower,
           sheet = "DF_Follower")
```


    ### ANALYZE


 ## TIKTOK
 

#AVOSKIN

# Hours Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "TIKTOK", Name == "Avoskin_Tiktok") %>% 
  group_by(Hour) %>% 
  summarise(total = n(), `Mean Engagement` = mean(Engagement)) %>% 
  arrange(desc(`Mean Engagement`))
```
# Time Background Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "TIKTOK", Name == "Avoskin_Tiktok") %>% 
  group_by(`Time Background`) %>% 
  summarise(Total = n(), `Mean engagement` = mean(Engagement), sum(Engagement)) %>% 
  arrange(desc(`Mean engagement`))
```


#Elsheskin

# Hours Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "TIKTOK", Name == "Elsheskin_Tiktok") %>% 
  group_by(Hour) %>% 
  summarise(total = n(), `Mean Engagement` = mean(Engagement)) %>% 
  arrange(desc(`Mean Engagement`))
```
# Time Background Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "TIKTOK", Name == "Elsheskin_Tiktok") %>% 
  group_by(`Time Background`) %>% 
  summarise(Total = n(), `Mean engagement` = mean(Engagement), sum(Engagement)) %>% 
  arrange(desc(`Mean engagement`))
```


#Somethinc

# Hours Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "TIKTOK", Name == "Somethinc_Tiktok") %>% 
  group_by(Hour) %>% 
  summarise(total = n(), `Mean Engagement` = mean(Engagement)) %>% 
  arrange(desc(`Mean Engagement`))
```
# Time Background Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "TIKTOK", Name == "Somethinc_Tiktok") %>% 
  group_by(`Time Background`) %>% 
  summarise(Total = n(), `Mean engagement` = mean(Engagement), sum(Engagement)) %>% 
  arrange(desc(`Mean engagement`))
```



## INSTAGRAM



#AVOSKIN

# Hours Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "INSTAGRAM", Name == "Avoskin_Instagram") %>% 
  group_by(Hour) %>% 
  summarise(total = n(), `Mean Engagement` = mean(Engagement)) %>% 
  arrange(desc(`Mean Engagement`))
```
# Time Background Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "INSTAGRAM", Name == "Avoskin_Instagram") %>% 
  group_by(`Time Background`) %>% 
  summarise(Total = n(), `Mean engagement` = mean(Engagement), sum(Engagement)) %>% 
  arrange(desc(`Mean engagement`))
```


#Elsheskin

# Hours Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "INSTAGRAM", Name == "Elsheskin_Instagram") %>% 
  group_by(Hour) %>% 
  summarise(total = n(), `Mean Engagement` = mean(Engagement)) %>% 
  arrange(desc(`Mean Engagement`))
```
# Time Background Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "INSTAGRAM", Name == "Elsheskin_Instagram") %>% 
  group_by(`Time Background`) %>% 
  summarise(Total = n(), `Mean engagement` = mean(Engagement), sum(Engagement)) %>% 
  arrange(desc(`Mean engagement`))
```


#Somethinc

# Hours Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "INSTAGRAM", Name == "Somethinc_Instagram") %>% 
  group_by(Hour) %>% 
  summarise(total = n(), `Mean Engagement` = mean(Engagement)) %>% 
  arrange(desc(`Mean Engagement`))
```
# Time Background Posts That Have the Highest Average Engagement
```{r}
df_post %>% 
  filter(Network == "INSTAGRAM", Name == "Somethinc_Instagram") %>% 
  group_by(`Time Background`) %>% 
  summarise(Total = n(), `Mean engagement` = mean(Engagement), sum(Engagement)) %>% 
  arrange(desc(`Mean engagement`))
```


      
      
      
      
      ######## PECAH DF POST
      
      
      
      
      
```{r}
df_post_avoskin <- df_post %>% 
  filter(Name == "Avoskin_Tiktok" | Name == "Avoskin_Instagram")


df_post_somethinc<- df_post %>% 
  filter(Name == "Somethinc_Tiktok" | Name == "Somethinc_Instagram")

df_post_elsheskin <- df_post %>% 
  filter(Name == "Elsheskin_Tiktok" | Name == "Elsheskin_Instagram")
```


#Make new variable named group that comes from grouping caption
#Avoskin
```{r}
df_post_avoskin <- df_post_avoskin %>%  
  mutate(Caption = tolower(Message)) %>% 
  mutate(group = case_when(grepl("webseries",Caption) ~ "Web Series",
                           grepl("web series",Caption) ~ "Web Series",
                           grepl("webseriesavoskin",Caption) ~ "Web Series",
                           grepl("meetavoskin",Caption) ~ "Meet Avoskin",
                           grepl("meet avoskin",Caption) ~ "Meet Avoskin",
                           grepl("offline event",Caption) ~ "Meet Avoskin",
                           grepl("challenge", Caption) ~ "Challenge",
                           grepl("tantang", Caption) ~ "Challenge",
                           grepl("giveaway", Caption) ~ "Giveaway",
                           grepl("bagi-bagi", Caption) ~ "Giveaway",
                           grepl("promo",Caption) ~ "Promo",
                           grepl("cashback",Caption) ~ "Promo",
                           grepl("hemat",Caption) ~ "Promo",
                           grepl("gratis",Caption) ~ "Promo",
                           grepl("potongan",Caption) ~ "Promo",
                           grepl("free",Caption) ~ "Promo",
                           grepl("potongan",Caption) ~ "Promo",
                           grepl("diskon",Caption) ~ "Promo",
                           grepl("sale",Caption) ~ "Promo",
                           grepl("tips",Caption) ~ "Recommendation",
                           grepl("rekomendasi",Caption) ~ "Recommendation",
                           grepl("kunci",Caption) ~ "Recommendation",
                           grepl("rahasia",Caption) ~ "Recommendation",
                           grepl("fungsi",Caption) ~ "Recommendation",
                           grepl("info",Caption) ~ "Recommendation",
                           grepl("bingung",Caption) ~ "Recommendation",
                           grepl("komen yuk",Caption) ~ "Interaction",
                           grepl("share yuk",Caption) ~ "Interaction",
                           grepl("first impression",Caption) ~ "Interaction",
                           grepl("pengalamanmu",Caption) ~ "Interaction",
                           grepl("konsultasi",Caption) ~ "Interaction",
                           grepl("sahabat avo?",Caption) ~ "Interaction",
                           grepl("dong",Caption) ~ "Interaction",
                           grepl("request",Caption) ~ "Interaction",
                           grepl("ygy",Caption) ~ "Interaction",
                           grepl("absen dulu",Caption) ~ "Interaction",
                           grepl("di bawah",Caption) ~ "Interaction",
                           grepl("relate",Caption) ~ "Interaction",
                           grepl("", Caption, ignore.case = TRUE) ~"Others"))
```

#Somethinc
```{r}
df_post_somethinc <- df_post_somethinc %>%  
  mutate(Caption = tolower(Message)) %>% 
  mutate(group = case_when(grepl("giveaway", Caption) ~ "Giveaway",
                           grepl("bagi-bagi", Caption) ~ "Giveaway",
                           grepl("promo",Caption) ~ "Promo",
                           grepl("cashback",Caption) ~ "Promo",
                           grepl("hemat",Caption) ~ "Promo",
                           grepl("gratis",Caption) ~ "Promo",
                           grepl("potongan",Caption) ~ "Promo",
                           grepl("free",Caption) ~ "Promo",
                           grepl("potongan",Caption) ~ "Promo",
                           grepl("diskon",Caption) ~ "Promo",
                           grepl("sale",Caption) ~ "Promo",
                           grepl("tips",Caption) ~ "Recommendation",
                           grepl("rekomendasi",Caption) ~ "Recommendation",
                           grepl("kunci",Caption) ~ "Recommendation",
                           grepl("kenapa sih",Caption) ~ "Recommendation",
                           grepl("kupas",Caption) ~ "Recommendation",
                           grepl("rahasia",Caption) ~ "Recommendation",
                           grepl("fungsi",Caption) ~ "Recommendation",
                           grepl("info",Caption) ~ "Recommendation",
                           grepl("bingung",Caption) ~ "Recommendation",
                           grepl("tutorial",Caption) ~ "Recommendation",
                           grepl("komen yuk",Caption) ~ "Interaction",
                           grepl("share yuk",Caption) ~ "Interaction",
                           grepl("first impression",Caption) ~ "Interaction",
                           grepl("pengalamanmu",Caption) ~ "Interaction",
                           grepl("konsultasi",Caption) ~ "Interaction",
                           grepl("sahabat avo?",Caption) ~ "Interaction",
                           grepl("dong",Caption) ~ "Interaction",
                           grepl("request",Caption) ~ "Interaction",
                           grepl("ygy",Caption) ~ "Recommendation",
                           grepl("absen dulu",Caption) ~ "Interaction",
                           grepl("di bawah",Caption) ~ "Interaction",
                           grepl("relate",Caption) ~ "Interaction",
                           grepl("", Caption, ignore.case = TRUE) ~"Others"))
```

#Elsheskin
```{r}
df_post_elsheskin<- df_post_elsheskin %>%  
  mutate(Caption = tolower(Message)) %>% 
  mutate(group = case_when(grepl("giveaway", Caption) ~ "Giveaway",
                           grepl("bagi-bagi", Caption) ~ "Giveaway",
                           grepl("hadiah", Caption) ~ "Giveaway",
                           grepl("promo",Caption) ~ "Promo",
                           grepl("cashback",Caption) ~ "Promo",
                           grepl("hemat",Caption) ~ "Promo",
                           grepl("gratis",Caption) ~ "Promo",
                           grepl("potongan",Caption) ~ "Promo",
                           grepl("free",Caption) ~ "Promo",
                           grepl("potongan",Caption) ~ "Promo",
                           grepl("diskon",Caption) ~ "Promo",
                           grepl("sale",Caption) ~ "Promo",
                           grepl("gift",Caption) ~ "Promo",
                           grepl("tips",Caption) ~ "Recommendation",
                           grepl("rekomendasi",Caption) ~ "Recommendation",
                           grepl("hati-hati",Caption) ~ "Recommendation",
                           grepl("kunci",Caption) ~ "Recommendation",
                           grepl("rahasia",Caption) ~ "Recommendation",
                           grepl("fungsi",Caption) ~ "Recommendation",
                           grepl("info",Caption) ~ "Recommendation",
                           grepl("optimal",Caption) ~ "Recommendation",
                           grepl("maksimal",Caption) ~ "Recommendation",
                           grepl("cari tahu",Caption) ~ "Recommendation",
                           grepl("fakta",Caption) ~ "Recommendation",
                           grepl("bingung",Caption) ~ "Recommendation",
                           grepl("solusi",Caption) ~ "Recommendation",
                           grepl("kesalahan",Caption) ~ "Recommendation",
                           grepl("hacks",Caption) ~ "Recommendation",
                           grepl("komen yuk",Caption) ~ "Interaction",
                           grepl("kurangin",Caption) ~ "Interaction",
                           grepl("share yuk",Caption) ~ "Interaction",
                           grepl("kasih tau",Caption) ~ "Interaction",
                           grepl("kasih tahu",Caption) ~ "Interaction",
                           grepl("comment",Caption) ~ "Interaction",
                           grepl("first impression",Caption) ~ "Interaction",
                           grepl("pengalamanmu",Caption) ~ "Interaction",
                           grepl("konsultasi",Caption) ~ "Interaction",
                           grepl("sahabat avo?",Caption) ~ "Interaction",
                           grepl("dong",Caption) ~ "Interaction",
                           grepl("request",Caption) ~ "Interaction",
                           grepl("ygy",Caption) ~ "Interaction",
                           grepl("absen dulu",Caption) ~ "Interaction",
                           grepl("di bawah",Caption) ~ "Interaction",
                           grepl("hayo",Caption) ~ "Interaction",
                           grepl("relate",Caption) ~ "Interaction",
                           grepl("nih?",Caption) ~ "Interaction",
                           grepl("", Caption, ignore.case = TRUE) ~"Others"))
```
  
```{r}
ndf_post <- rbind(df_post_elsheskin, df_post_avoskin, df_post_somethinc)
```
      
      
      
      ### Load Data



#Input JSON from API Key.
```{r}
gs4_auth(path = "my_api_key.json")
```

#Assign the Docs into Variable gsheets.
```{r}
gsheet <- gs4_get("https://docs.google.com/spreadsheets/d/1S76OPrihc4NB52MzR7jsLZNGIrrak8HeIOnmMwucYhs/edit#gid=1383616703")
```

#Put the Data to the Sheets in the test Google Sheets we have.
```{r}
range_write(gsheet,
            df_post_avoskin,
            sheet = "NDF_Post")
```



















